% Created 2023-03-16 Thu 21:23
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Andrew Tropin}
\date{\today}
\title{The First Proposal}
\hypersetup{
 pdfauthor={Andrew Tropin},
 pdftitle={The First Proposal},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 30.0.50 (Org mode 9.6.1)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\part{What needed}
\label{sec:org5d1179e}
\chapter{For Project}
\label{sec:org6f603c5}
First phase:
\begin{itemize}
\item Community.
\item Attention via functional DevOps.
\item Reproducible Emacs distribution.
\item Port of Emacs distro to pinephone and raspberry.
\end{itemize}

Second phase:
\begin{itemize}
\item Cross-platform content-addressable distributed storage.
\item Ports of CPCADS to Platforms (pinephone for example), to get more attention through the mobile OS trend.
\item Import of current code to CPCADS.
\end{itemize}

\chapter{For Team}
\label{sec:org3aeaa0a}
\begin{itemize}
\item Knowledge and skills on Lisp, RDD, TDD.
\item On FP.
\item On Guix and FPM.
\end{itemize}

\part{We can}
\label{sec:org6bb4aed}
Prepare team for the Project.
\begin{itemize}
\item Setup a team to use Guix, Guile.
\item Dog fooding with Guix -> introduction to lisp, taste of fp, fpm + same dev
environment (easier to share work).
\item Find, make and share materials on lisp, Guix and provide support.
\end{itemize}

Primary courses:
\begin{itemize}
\item Theoretical FP 1 (Scheme, quoting, macros) 1 week.
\item Guix (Packaging, API, Services mechanism, Features mechanism, part of G-exps)
1 week.
\end{itemize}

Additional courses:
\begin{itemize}
\item Practical FP (RDD, TDD, Structured Side-Effects, Monads, G-exps) 1 week.
\item Theoretical FP 2 (lambda calculus, SICP) 1 week.
\end{itemize}

On consulting:
\begin{itemize}
\item Do a consulting and help to solve hard problems, designing architecture,
managing development and reducing waste.
\item Help with Emacs Distro Development.
\item Help with preparing patches for Guix/rde/Emacs.
\end{itemize}

I plan to keep working on anyway:
\begin{description}
\item[{Develop guile-tree-sitter}] useful for import to CPCADS.
\item[{Develop gider, a scheme dev environment}] useful for guile development, but
later can be used as dev environment for CPCADS.
\item Develop functional DevOps tooling.
\end{description}

\part{The Value}
\label{sec:org854bb83}
\chapter{Education}
\label{sec:orgbb28f65}
avg middle dev salary: 80k euro/y -> 6.6k/m,
4 people learning for one month will cost \textasciitilde{}27k/m.

I can teach the same 4 times faster:
1 week course will cost 22k. It saves \textasciitilde{}5k euro and 3 weeks.

\chapter{Consulting}
\label{sec:orgf613bb6}
4 full days of consulting for 5k/m.

Think about result-based consulting.
\end{document}